### 2018-08-28 pilot_manuscript.Rmd
updates for pilot study

##stem the original MFD stuff - separate loop on only the mfd data frame
for(i in 1:nrow(original_mfd)) {
  original_mfd$h2hi[i] = stemDocument(original_mfd$h2hi[i], language = "english")
  original_mfd$h2lo[i] = stemDocument(original_mfd$h2lo[i], language = "english")
  original_mfd$f2hi[i] = stemDocument(original_mfd$f2hi[i], language = "english")
  original_mfd$f2lo[i] = stemDocument(original_mfd$f2lo[i], language = "english")
  original_mfd$i2hi[i] = stemDocument(original_mfd$i2hi[i], language = "english")
  original_mfd$i2lo[i] = stemDocument(original_mfd$i2lo[i], language = "english")
  original_mfd$a2hi[i] = stemDocument(original_mfd$a2hi[i], language = "english")
  original_mfd$a2lo[i] = stemDocument(original_mfd$a2lo[i], language = "english")
  original_mfd$p2hi[i] = stemDocument(original_mfd$p2hi[i], language = "english")
  original_mfd$p2lo[i] = stemDocument(original_mfd$p2lo[i], language = "english")
}

final$hhisum = NA
final$hlosum = NA
final$fhisum = NA
final$flosum = NA
final$ihisum = NA
final$ilosum = NA
final$ahisum = NA
final$alosum = NA
final$phisum = NA
final$plosum = NA

for (i in 1:nrow(final)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
##find the rows that match the mfd list and sum and save
final$hsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2hi[original_mfd$h2hi != "" & original_mfd$h2hi != "NA"])])
final$hsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2lo[original_mfd$h2lo != "" & original_mfd$h2lo != "NA"])])

final$fsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2hi[original_mfd$f2hi != "" & original_mfd$f2hi != "NA"])])
final$fsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2lo[original_mfd$f2lo != "" & original_mfd$f2lo != "NA"])])

final$isumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2hi[original_mfd$i2hi != "" & original_mfd$i2hi != "NA"])])
final$isumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2lo[original_mfd$i2lo != "" & original_mfd$i2lo != "NA"])])

final$asumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2hi[original_mfd$a2hi != "" & original_mfd$a2hi != "NA"])])
final$asumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2lo[original_mfd$a2lo != "" & original_mfd$a2lo != "NA"])])

final$psumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2hi[original_mfd$p2hi != "" & original_mfd$p2hi != "NA"])])
final$psumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2lo[original_mfd$p2lo != "" & original_mfd$p2lo != "NA"])])
}

final$hperhi = final$hsumhi / final$wordcount * 100
final$hperlo = final$hsumlo / final$wordcount * 100
final$fperhi = final$fsumhi / final$wordcount * 100
final$fperlo = final$fsumlo / final$wordcount * 100
final$iperhi = final$isumhi / final$wordcount * 100
final$iperlo = final$isumlo / final$wordcount * 100
final$aperhi = final$asumhi / final$wordcount * 100
final$aperlo = final$asumlo / final$wordcount * 100
final$pperhi = final$psumhi / final$wordcount * 100
final$pperlo = final$psumlo / final$wordcount * 100

#let's look at the means
tapply(final$hperhi, final$Source, mean)
tapply(final$hperlo, final$Source, mean)
tapply(final$fperhi, final$Source, mean)
tapply(final$fperlo, final$Source, mean)
tapply(final$iperhi, final$Source, mean)
tapply(final$iperlo, final$Source, mean)
tapply(final$aperhi, final$Source, mean)
tapply(final$aperlo, final$Source, mean)
tapply(final$pperhi, final$Source, mean)
tapply(final$pperlo, final$Source, mean)
```

>>>>

# ##stem the original MFD stuff - separate loop on only the mfd data frame
# for(i in 1:nrow(original_mfd)) {
#   original_mfd$h2hi[i] = stemDocument(original_mfd$h2hi[i], language = "english")
#   original_mfd$h2lo[i] = stemDocument(original_mfd$h2lo[i], language = "english")
#   original_mfd$f2hi[i] = stemDocument(original_mfd$f2hi[i], language = "english")
#   original_mfd$f2lo[i] = stemDocument(original_mfd$f2lo[i], language = "english")
#   original_mfd$i2hi[i] = stemDocument(original_mfd$i2hi[i], language = "english")
#   original_mfd$i2lo[i] = stemDocument(original_mfd$i2lo[i], language = "english")
#   original_mfd$a2hi[i] = stemDocument(original_mfd$a2hi[i], language = "english")
#   original_mfd$a2lo[i] = stemDocument(original_mfd$a2lo[i], language = "english")
#   original_mfd$p2hi[i] = stemDocument(original_mfd$p2hi[i], language = "english")
#   original_mfd$p2lo[i] = stemDocument(original_mfd$p2lo[i], language = "english")
# }
# 
# final$hhisum = NA
# final$hlosum = NA
# final$fhisum = NA
# final$flosum = NA
# final$ihisum = NA
# final$ilosum = NA
# final$ahisum = NA
# final$alosum = NA
# final$phisum = NA
# final$plosum = NA
# 
# for (i in 1:nrow(final)) {
# ##first make a table of a response, unlisting everything
# temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
# ##find the rows that match the mfd list and sum and save
# final$hsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2hi[original_mfd$h2hi != "" & original_mfd$h2hi != "NA"])])
# final$hsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2lo[original_mfd$h2lo != "" & original_mfd$h2lo != "NA"])])
# 
# final$fsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2hi[original_mfd$f2hi != "" & original_mfd$f2hi != "NA"])])
# final$fsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2lo[original_mfd$f2lo != "" & original_mfd$f2lo != "NA"])])
# 
# final$isumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2hi[original_mfd$i2hi != "" & original_mfd$i2hi != "NA"])])
# final$isumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2lo[original_mfd$i2lo != "" & original_mfd$i2lo != "NA"])])
# 
# final$asumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2hi[original_mfd$a2hi != "" & original_mfd$a2hi != "NA"])])
# final$asumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2lo[original_mfd$a2lo != "" & original_mfd$a2lo != "NA"])])
# 
# final$psumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2hi[original_mfd$p2hi != "" & original_mfd$p2hi != "NA"])])
# final$psumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2lo[original_mfd$p2lo != "" & original_mfd$p2lo != "NA"])])
# }
# 
# final$hperhi = final$hsumhi / final$wordcount * 100
# final$hperlo = final$hsumlo / final$wordcount * 100
# final$fperhi = final$fsumhi / final$wordcount * 100
# final$fperlo = final$fsumlo / final$wordcount * 100
# final$iperhi = final$isumhi / final$wordcount * 100
# final$iperlo = final$isumlo / final$wordcount * 100
# final$aperhi = final$asumhi / final$wordcount * 100
# final$aperlo = final$asumlo / final$wordcount * 100
# final$pperhi = final$psumhi / final$wordcount * 100
# final$pperlo = final$psumlo / final$wordcount * 100
# 
# #let's look at the means
# tapply(final$hperhi, final$Source, mean)
# tapply(final$hperlo, final$Source, mean)
# tapply(final$fperhi, final$Source, mean)
# tapply(final$fperlo, final$Source, mean)
# tapply(final$iperhi, final$Source, mean)
# tapply(final$iperlo, final$Source, mean)
# tapply(final$aperhi, final$Source, mean)
# tapply(final$aperlo, final$Source, mean)
# tapply(final$pperhi, final$Source, mean)
# tapply(final$pperlo, final$Source, mean)
```

```{r new_data, include = FALSE}
#take final$stemmed column loop over this

harm_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

for (i in 1:nrow(final)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(harmstuffthing$words[harmstuffthing$words != "" & harmstuffthing$words != "NA"])]

#add to the dataset
temp2$URL = final$Url[i]
temp2$Source = final$Source[i]
temp2$wordcount = final$wordcount[i]

#bind with original
harm_final_data = rbind(harm_final_data, temp2)
}
